\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{float}
\usepackage{setspace}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,shapes.geometric}

\title{City1 v2: A Reproducible Open-Data Calibrated Proxy Population Surface Baseline with Multi-Level Validation for Intra-Urban Analysis in Kazakhstan}
\author{}
\date{}

\begin{document}

\maketitle

\begin{abstract}
Accurate intra-urban population surfaces are difficult to construct in settings where grid-level census labels are unavailable. We present City1 v2, a reproducible open-data baseline for proxy population surface modeling in Kazakhstan. The system combines OpenStreetMap-derived features with weak supervision on a frozen 500 m grid and calibrates cell-level predictions to official city population totals. The resulting surface is evaluated through a multi-level validation framework comprising leave-one-city-out transfer testing, spatial block cross-validation, grid-size benchmarking, OSM completeness assessment, partial internal administrative comparison at the district level, external structural comparison against WorldPop and GHS-POP, feature-family ablation, and qualitative hotspot/coldspot review. In the frozen production configuration, the random forest model outperforms ridge under leave-one-city-out validation, achieving a calibrated RMSE of 115.934 and a calibrated $R^2$ of 0.934. External comparison supports structural plausibility: WorldPop provides the strongest overall correlation, whereas GHS-POP aligns more closely with dense hotspot structure. Ablation results show that built-form signals are the dominant reduced predictor family, although the full feature set remains strongest and calibration materially improves the final surface. Rather than optimizing for a single benchmark or claiming truth reconstruction, City1 v2 makes credibility under missing cell-level truth explicit through official-total calibration, a frozen reproducible workflow, and multi-level validation. The result is a transparent, calibrated, and bounded baseline for intra-urban analysis in data-scarce urban settings.
\end{abstract}

\input{sections/01_introduction.tex}
\input{sections/02_related_work.tex}
\input{sections/03_study_design_and_data.tex}
\input{sections/04_method.tex}
\input{sections/05_validation_framework.tex}
\input{sections/06_results.tex}
\input{sections/07_limitations.tex}
\input{sections/08_conclusion.tex}
\input{sections/09_data_and_code_availability.tex}

\bibliographystyle{plain}
\bibliography{refs}

\end{document}
